Testing the precision of Bangla Communication Scale: Item Response Theory Guided Analysis

### 2022-02-01 manuscript.Rmd
Strudy-1 participants description added

des.2 <- desc %>% 
  psych::describeBy("Gender")
female <- as.tibble(des.2$Female)
male <- as.tibble(des.2$Male)

@@

A cross-sectional survey was used to collect data from a large sample of students of grade 8-10 (n = `r nrow(efa.data)`) from ---- schools following convenience sampling method. T. For estimating the sample size for the CFA we followed the N:q rule [@RN1268; @RN1269; @RN1270; @RN1271] where 10 participants per parameters is required to earn trustworthiness of the result. Our sample size exceeds the requirement. Among `r nrow(data)` participants, `r female[1,2]` were female aged between `r female[4,8]` to `r female[4,9]` years (`r round(female[4,3],2)`±`r round(female[4,4],2)`). `r male[1,2]`  were male with an age range between `r male[4,8]` to `r male[4,9]` years (`r round(male[4,3],2)`±`r round(male[4,4],2)`). Table \@ref(tab:demographics) summarizes the demographics.

>>>>

des.2 <- desc %>% 
  psych::describeBy("Gender")
female <- as.tibble(des.2$Girl)
male <- as.tibble(des.2$Boy)

@@

A cross-sectional survey was used to collect data from a large sample of students of grade 8-10 (n = `r nrow(efa.data)`) from ---- schools following convenience sampling method. T. For estimating the sample size for the CFA we followed the N:q rule [@RN1268; @RN1269; @RN1270; @RN1271] which required 10 participants per parameters for trustworthiness of the result. Our sample size exceeds the requirement. Among `r nrow(efa.data))` participants, `r female[1,2]` were female aged between `r female[2,8]` to `r female[2,9]` years (`r round(female[2,3],2)`±`r round(female[2,4],2)`). `r male[1,2]`  were male with an age range between `r male[2,8]` participants `r male[2,9]` years (`r round(male[2,3],2)`±`r round(male[2,4],2)`). `r desc_tibble [4,2]` participants belonged to middle socio-economic status. `r desc_tibble [3,2]` and `r desc_tibble [5,2]` participants belonged to lower and upper socio-economic status-respectively.
